\documentclass[11pt]{article}
\usepackage[margin = 0.75in]{geometry}
\usepackage{amsmath, amssymb, amsthm, amsfonts}
\usepackage[none]{hyphenat}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage[nottoc, notlot, notlof]{tocbibind}


\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\textsl{ SoS 2020 }}
\fancyhead[C]{Plan of Action}
\fancyhead[R]{ \textsl{ Coding Theory }}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\begin{titlepage}
\begin{center}
\vspace{1cm}
\Large{\textsf{ Summer of Science, 2020 }} \\
\vspace{1.5mm}
\large{\textsf{ MnP Club, IIT Bombay }}
\vfill
\line(1,0){400} \\[2mm]
\Huge{\textsc{ Coding Theory }}\\[3mm]
\Large{\textbf{- Plan of Action -}}\\[1mm]
\line(1,0){400} \\
\vfill
\textsf{Abhinav Gupta} \footnote{ Mentored by \textsf{Shourya Pandey} }\\
\textsf{April 10, 2020} \\
\end{center}
\end{titlepage}

\section*{Overview}
I'll be mainly covering the book \textit{A First Course in Coding Theory} by \textit{Raymond Hill} as suggested by my mentor. My main objective will be to cover the basics of coding theory, and side-by-side learning the mathematical background, as I progress.

\section*{Chapters of the book}
These are the chapters of the suggested book which I intend to cover as a part of this year's SoS.
\begin{enumerate}
	\itemsep-1mm
    \item Introduction to error-correcting codes 
    \item The main coding theory problem
    \item An introduction to finite fields
    \item Vector spaces over finite fields
    \item Introduction to linear codes
    \item Encoding and decoding with a linear code
    \item The dual code, the parity-check matrix, and syndrome
    \item The Hamming codes
    \item Perfect codes
    \item Codes and Latin squares
    \item A double-error correcting decimal code and an introduction to BCH codes
    \item Cyclic codes
	\item Weight enumerators
\end{enumerate}
I'll definitely want to finish the book, but after covering two introductory chapters and talking to the mentor, it seems like these topics will take more time than I expected. I'll try my best to cover as much as possible.

\section*{Weekly Goals}
I have already covered 2 introductory chapters. Also, I have repeated the same chapters two weeks several times as I’m planning to cover that chapter somewhere in the middle of the two weeks.\\
More or less, I'll follow this schedule :-

\begin{itemize}
	\item Week 1 : \textit{April 11, 2020 - April 17, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 3
		\item Chapter 4
		\item Chapter 5
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Week 2 : \textit{April 18, 2020 - April 24, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 6
		\item Chapter 7
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Week 3 : \textit{April 25, 2020 - May 1, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 7
		\item Till Chapter 7 in Mid-summer report (\textit{April 30, 2020})
		\item Chapter 8
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Week 4 : \textit{May 2, 2020 - May 8, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 8
		\item Chapter 9
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Week 5 : \textit{May 9, 2020 - May 15, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 9
		\item Chapter 10
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Week 6 : \textit{May 16, 2020 - May 22, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 10
		\item Chapter 11
	\end{itemize}
\end{itemize}

\begin{itemize}
	\item Week 7 : \textit{May 23, 2020 - May 29, 2020}
	\begin{itemize}
		\itemsep-1mm
		\item Chapter 12
		\item Chapter 13
	\end{itemize}
\end{itemize}

\section*{Learning \LaTeX\ }
During this project work, I'll also be learning \LaTeX\ (this is the the first implementation). Here, I'll like to thank \textit{Aryaman Maithani} for all the \LaTeX\ realted material he provided (not only for \LaTeX\ though), through his website. It definitely helped a lot.

\end{document}